### 2020-12-17 README.Rmd
profiled get_us_covid
tests

removed testes

removed testes2

removed tests covid

test_getus

us_test separated

prodiled function get_covid and fixed tests

[![](https://img.shields.io/badge/devel%20version-0.0.1.200-blue.svg)](https://codecov.io/gh/c1au6i0/covid19census?branch=master)
[![Build Status](https://travis-ci.com/c1au6i0/covid19census.svg?branch=master)](https://travis-ci.com/c1au6i0/covid19census)
[![Codecov test coverage](https://codecov.io/gh/c1au6i0/covid19census/branch/master/graph/badge.svg)](https://codecov.io/gh/c1au6i0/covid19census?branch=master)

>>>>

[![](https://img.shields.io/badge/devel%20version-0.0.1.300-blue.svg)](https://codecov.io/gh/c1au6i0/covid19census?branch=master)
[![Build Status](https://travis-ci.com/c1au6i0/covid19census.svg?branch=master)](https://travis-ci.com/c1au6i0/covid19census)
[![Codecov test coverage](https://codecov.io/gh/c1au6i0/covid19census/branch/master/graph/badge.svg)](https://codecov.io/gh/c1au6i0/covid19census?branch=master)
